---
title: "Country-Data"
output: html_document
---

1. how many ids matched in the merge?
```{r}
countries = read.csv('data/Countries.csv')
nrow(countries)
original.education.data = read.csv('data/education-raw.csv')
nrow(original.education.data)
```
2. Sort by gdp (so US is last). What is the 13th country?

```{r}
countries[order(countries$GDP),][13,]
```

3. What are the average GDP rankings for the "High Income: OECD" and "High income nonOECD" groups?
... NAs removed

```{r}
mean(countries[countries$IncomeGroup == 'High income: nonOECD' & complete.cases(countries$GDP),]$GDP)
mean(countries[countries$IncomeGroup == 'High income: OECD' & complete.cases(countries$GDP),]$GDP)
```

4. Plot the GDP for all of the countries. Use ggplot2 - color by IncomeGroup

```{r}
#install.packages('ggplot2')
library('ggplot2')
#plot(countries$GDP)
not.null.countries = countries[countries$IncomeGroup != '' & complete.cases(countries$GDP),]
ggplot(not.null.countries, aes(x=CountryCode, y=GDP, colour=IncomeGroup)) + geom_point() + scale_fill_manual(values=c('#CC6666', '#9999CC', '#66CC99', '#3c0', 'c65', '3c9'))
```
5. Seperate GDP rankings into 5 quantile groups. Make a table versus Income Group. how many countries are Lower middle income among the 38 nations with the highest GDP?
```{r}
first.quantile = not.null.countries[1:38,]
countries.in.lower.income = first.quantile[first.quantile$IncomeGroup == 'Lower middle income',]
nrow(countries.in.lower.income)
```
