---
title: "MakeFile"
output: html_document
---

```{r, echo=FALSE}
# remove the data directory for presentation
unlink('data', recursive = TRUE)
```

### Download necessary data

Download the two required csv files (as `education-raw.csv` and `gdp-raw.csv`).

```{r}
source('download.R')
```

### Tidy data

Create a new file `gdp-clean.csv` by taking the country code and gdp from `gdp-raw.csv`, while making sure that gdp is actually numerical and removing rows where GDP is `NA` (122 rows removed). Also, create `education-clean.csv` from the file `education-clean` by removing rows where Income Group is empty (6 rows removed).

```{r}
source('tidy.R')
```

### Merge data

Merge the data from `education-raw.csv` and `gdp-clean.csv` using the column "CountryCode". Create a new csv file `Countries.csv` based on only the three columns we need for analytics.

```{r}
source('merge.R')
```

### Install Packages

Be sure to install the following package if you want to replicate this study:

```{r}
#install.packages('ggplot2')
```
